Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales

### 2015-07-29 paper.tex
Updating figures and code
Edits to paper

The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the data associated with \cite{Denton}, with data available from 1980-1991; all other parameters are from \cite{Reconstruction} over the time range of 1972-2013, which are on a 1-hour time grid.  In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time, the value from GOES 7 was selected to avoid overlapping data points.  $\rho_{eq}$ is the inferred mass density based on the 3rd harmonic frequency of magnetic field measurements.  The smallest cadence for $\rho_{eq}$ values is 10 minutes.  To compute an hourly average over the same time range as the solar wind parameters, the median of all values in a given hourly range was used.  Fill values were used for hours when no measurements were available.

In this work events are considered when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in \ref{AllData}.  In finding events, all fill values were replaced with linearly interpolated values.  Figure \ref{AllData} shows the values of $B_Z$, $V_{SW}$, $D_{st}$, $F_{10.7}$, and Mass Density for the duration of the dataset.

@@

\begin{figure}[htp]
\centering
\includegraphics[scale=0.45]{paperfigures/alldata.eps}
\caption{Overview of data used in this study. The top four panels are from \cite{Reconstruction} and the bottom panel is based on \cite{Denton} after interpolation and averaging described in the text. Dashed horizontal lines indicate default event cutoff thresholds.}
\label{AllData}
\end{figure}

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.42]{paperfigures/DstMDAllData.eps}
\includegraphics[scale=0.42]{paperfigures/ccplot.eps}
\includegraphics[scale=0.42]{paperfigures/DSTvsMD.eps}
\caption{(a) All data of $D_{st}$ and $\rho_{eq}$ (b) Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$. (c) $D_{st}$ against $\rho_{eq}$ at one hour and one-day median values.  }
\label{ccplot}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-50-tak.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-day.eps}
\caption{(a) Verifying \cite{Takahashi2010} Fig. 11 conditions: $D_{st}<-50nT$ between 1989 and 1991 and (b) One-day medians of $D_{st}$ events at a threshold of $-40nT$}
\label{DailyAverages}
\end{figure}

>>>>

The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980-1991; all other parameters are from \cite{Reconstruction} over the time range of 1972-2013, which are on a 1-hour time grid. $\rho_{eq}$ is the inferred mass density based on the 3rd harmonic frequency of magnetic field measurements.  The smallest cadence for $\rho_{eq}$ values is 10 minutes.  To compute an hourly average over the same time range as the solar wind parameters, the median of all values in a given hourly range was used.  Fill values were used for hours when no measurements were available.  In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 7 was selected to avoid overlapping data points.  An overview of the data is given in Figure~\ref{AllData}.

In this work events defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in by horizontal dashed lines in the respective panels of Figure~\ref{AllData}.  In finding events, all fill values were replaced with linearly interpolated values.  Figure \ref{AllData} shows the values of $B_z$, $V_{SW}$, $D_{st}$, $F_{10.7}$, and Mass Density for the duration of the dataset.

@@

\begin{figure}[htp]
\centering
\includegraphics[scale=0.45]{paperfigures/alldata.eps}
\caption{Overview of data used in this study. The top four panels show parameters from \cite{Reconstruction} and the bottom panel is based on $\rho_{eq}$ from \cite{Denton} after interpolation and averaging described in the text. Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st}=-50~nT$ and $\rho_{eq}$=40~amu/cm^3$}.
\label{AllData}
\end{figure}

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.42]{paperfigures/F107MDAllData.eps}
\includegraphics[scale=0.42]{paperfigures/ccplot.eps}
\includegraphics[scale=0.42]{paperfigures/F107vsMD.eps}
\caption{(a) All data of $D_{st}$ and $\rho_{eq}$ (b) Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$. (c) $D_{st}$ against $\rho_{eq}$ at one hour and one-day median values.  }
\label{ccplot}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-50-tak.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-day.eps}
\caption{(a) Verifying \cite{Takahashi2010} Fig. 11 conditions: $D_{st}<-50nT$ between 1989 and 1991 and (b) Same as (a) but for 1987 to 1991, and not just pre-noon events}
\label{DailyAverages}
\end{figure}
